VIPE: Virtualized Intermittently-Powered Executor

### 2017-07-17 paper/iposDataProtection.tex
iposDataProtection error corrected

\subsubsection{ Direct Memory Access Based Protection Method (better name is needed)}
%
	\begin{figure}[t]
		\centering
         \subfigure[The time needed to transfer a block of data using pointers versus Direct Memory Access (DMA).]{\includegraphics[width=0.48\columnwidth]{figures/dmaSize_time.eps} }
	     \subfigure[The energy needed to transfer a block of data using pointers versus Direct Memory Access (DMA).]{\includegraphics[width=0.48\columnwidth]{figures/energyConsumptionDMA_SW.eps}}
		\caption{Time and energy consumption of moving a block of data from SRAM to FRAM}
		\label{fig:dmaTimeEnergy}
	\end{figure}
%
	Since accessing/updating buffers is more costly than directly accessing FRAM, at least without specialized hardware~\cite{clank}, we introduce the second method to apply the virtualization principle to the Modular Execution Model. This method utilizing the Direct Memory Access (DMA) Module. As Fig.~\ref{fig:dmaTimeEnergy} shows that DMA is much more efficient in transferring a block of data than the conventional (pointer based) way from the energy and time perspectives.

>>>>

\subsubsection{ Direct Memory Access Based Protection Method (better name is needed)}
%
	\begin{figure}[t]
		\centering
         \subfloat[The time needed to transfer a block of data using pointers versus Direct Memory Access (DMA).]{\includegraphics[width=0.48\columnwidth]{figures/dmaSize_time.eps} }
	     \subfloat[The energy needed to transfer a block of data using pointers versus Direct Memory Access (DMA).]{\includegraphics[width=0.48\columnwidth]{figures/energyConsumptionDMA_SW.eps}}
		\caption{Time and energy consumption of moving a block of data from SRAM to FRAM}
		\label{fig:dmaTimeEnergy}
	\end{figure}
%
	Since accessing/updating buffers is more costly than directly accessing FRAM, at least without specialized hardware~\cite{clank}, we introduce the second method to apply the virtualization principle to the Modular Execution Model. This method utilizing the Direct Memory Access (DMA) Module. As Fig.~\ref{fig:dmaTimeEnergy} shows that DMA is much more efficient in transferring a block of data than the conventional (pointer based) way from the energy and time perspectives.
